On the combination of Set Functions and Failures

### 2014-08-22 docs/src/usage.tex
currytools updated, bin/curry added

\subsection{Command of \CYS}
\label{sec:kics2-commands}

@@

\item[\fbox{\code{:show}}]\pindex{:show}
Show the source text of the currently loaded Curry program.
If the variable \code{showcommand} is set in the
configuration file \ccode{.kics2rc}
(see Section~\ref{sec-customization}),
its value is used as a command to show the source text,
otherwise the \ccode{cat} is used.

>>>>

\subsection{Commands of \CYS}
\label{sec:kics2-commands}

@@

\item[\fbox{\code{:show}}]\pindex{:show}
Show the source text of the currently loaded Curry program.
If the variable \code{showcommand} is set in the
configuration file \ccode{.kics2rc}
(see Section~\ref{sec-customization}),
its value is used as a command to show the source text,
otherwise the command \ccode{cat} is used.
